%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\PassOptionsToPackage{pdfpagelabels=false}{hyperref} 
\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue, modroman]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

	
\usepackage[sc]{mathpazo}
\linespread{1.05}
\usepackage[T1]{fontenc}
%\usepackage[dvipsnames]{xcolor}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%\usepackage{hyperref}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\setlength{\topmargin}{-0.7in}
\usepackage{calc}
\setlength{\textheight}{\textheight+0.5in}
\usepackage{layout}
%\usepackage{hyperref}
\usepackage{color}
%\hypersetup{linkbordercolor = green}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Olalekan}
\familyname{Ogunmolu}
\definecolor{light-blue}{rgb}{0.30,0.35,1}
\title{Control Systems | Robotics | Machine Learning \newline
\textbf{\textcolor{light-blue}{\footnotesize 
Rerum Cognoscere Causas: To know the causes of things.} }}                               % optional, remove/comment the line if not wanted
\address{102 Lowell Rd}{North Reading, MA 01864, USA}{}         % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty 
%\fax{fax number}                             % optional, remove/comment the line if not wanted
\email{patlekano@gmail.com}                               % optional, remove/comment the line if not wanted
%\homepage{http://lakehanne.github.io}                         % optional, remove/comment the line if not wanted
%\extrainfo{\footnotesize http://ecs.utdallas.edu/$\sim$olalekan.ogunmolu/} 
\extrainfo{\footnotesize http://ecs.utdallas.edu/ $\sim$ opo140030}                 % optional, remove/comment the line if not wanted
%\photo[64pt][0.4pt]{EverPat}                       % optional, uncomment the line if wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Rerum Cognoscere Causas: To know the causes of things.}                                  % optional, remove/comment the line if not wanted
%

	
	
\begin{document}
	\long\def\/*#1*/{}								% Define block comment
%\vspace{-2ex}
	%-----       resume       ---------------------------------------------------------
	\makecvtitle
	\iffalse
	\section{Research Thrusts}
	\cvitem{}{Robots design and control, visual-servoing control, system identification, hardware verification. My research focuses on designing control algorithms and vision sensing systems for biomedical robots. I am interested in the applications of deep reinforcement learning to control.}
	\fi
	\section{Education}
	\cventry{2014--Present}{PhD in Electrical Engineering }{University of Texas at Dallas}{Richardson}{United States}
	{} % arguments 3 to 6 can be left empty
	
	\cventry{2011--2012}{Master of Science in Engineering in Control Systems}{The University of Sheffield}{Sheffield}{United Kingdom}{}
	
	\cventry{2000--2005}{Bachelor Of Science in Physics \& Electronics}{Adekunle Ajasin University}{Akungba}{Nigeria}{}

	\section{Publications}
	\cvitem{}{\textbf{Olalekan Ogunmolu, Ajith Venkateswaran, and Nicholas Gans}. \href{http://lakehanne.github.io/downloads/ICRA2017.pdf}{\textcolor{blue}{Learning deep neural network policies for head and neck motion control in cancer radiotherapy}}. To appear in \textit{IEEE Robotics and Automation Letters} (RA-L)/\emph{IEEE International Conference on Robotics and Automation (ICRA 2017)}, Singapore, June 2017.}{}
			
		\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nicholas Gans. \href{http://lakehanne.github.io/downloads/CASE2016.pdf}{\textcolor{blue}{Visual-servoing control of a soft-robot}}. To appear in: \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Fort-Worth, Texas, August 2016.}{}
			
		\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nicholas Gans. \href{http://lakehanne.github.io/downloads/CASE2015_Soft_Robot.pdf}{\textcolor{blue}{A Real-Time Soft-Robotic Patient Positioning System for Maskless Head-and-Neck Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Gothenburg, Sweden, August 2015.}{}
		
		\cvitem{}{\textbf{Olalekan Ogunmolu}, Nicholas Gans, Steve Jiang, Xuejun Gu. \href{http://www.aapm.org/meetings/2015AM/PRAbs.asp?mid=99&aid=29621}{\textcolor{blue}{An Image-Guided Soft Robotic Patient Positioning System for Maskless Head-And-Neck Cancer Radiotherapy: A Proof-of-Concept Study}}. \emph{American Association of Physicists in Medicine (AAPM)} Annual Meeting, July 2015.}{}
		\iffalse
		\cvitem{}{\textbf{Olalekan Ogunmolu}, \href{http://lakehanne.github.io/downloads/MS_Thesis.pdf}{\textcolor{blue}{Autonomous Navigation of a Rotor-craft unmanned aerial vehicle using machine vision.}} . \newline {MS Thesis, August. 2011. Advisor: Tony J. Dodd, University of Sheffield, England.}}{}
			
		\cvitem{}{\textbf{Olalekan Ogunmolu}, \href{http://lakehanne.github.io/downloads/BS_Thesis.pdf}{\textcolor{blue}{Single Fractional Parentage Coefficients in the sd-Shell Nuclei}} . \newline {BS Thesis, Nov. 2004. \hspace{0.5em} Advisor: Ademola Amusa, Adekunle Ajasin University, Nigeria.}}{}
		
	
	\section{Research Talks}
	\cvitem{}{Towards automated accurate patient positioning in maskless cancer radiotherapy. \emph{IEEE Computational Intelligence Society,} Fort Worth Chapter, TX, USA. December 2015.}
	\fi
	\section{Experience}
	\subsection{Research}
	\cventry{Spring - Summer '16 }{\textbf{Hardware Integration Intern, Amazon Robotics LLC}}{North Reading}{MA. USA}{$\bullet$ Wrote the ROS codebase for line scanners used in robots' pick and place tasks. 
		\newline $\bullet$ Wrote test cases, and defined test procedures for 2D and 3D sensors required on the new stow and sort robot development stations at Amazon Fulfillment Centers.
		\newline
		$\bullet$ Contributed wikis  to the kiva Systems confluence webpage and a model predictive controller "HowTO" to the kiva Systems knowledge base.}{}
		
	\cventry{Fall '14 - '15}{\textbf{Research Assistant}}{}{Sensing Robotics vision, Control and Estimation (SeRViCE) Lab}{}{Electrical Engineering Department, UT Dallas Richardson, TX \newline
	$\bullet$ Proof-of-concept design and rigorous testing of soft-robot system to be used in \textbf{intensity modulated radiotherapy (IMRT)}
	\newline
	$\bullet$ Procured and integrated mechanical hardware, vision components and software design for controlling patient head motion during IMRT simulation
	\newline
	$\bullet$ Achieved a sub-millimeter accuracy using multisensor kalman fusion in head motion tracking; optimized and parallelized algorithm in CUDA to speed up real-time head motion detection rates
	\newline
	$\bullet$ Implemented an LQG controller in LabVIEW based on the kalman filter estimate and achieved $\pm$1.5mm accuracy at head and neck 1-DOF motion control in clinical radiotherapy}
	\iffalse		
	\section{Mentoring}
	\subsection{Research mentoring}
	\cvline{Spring 2015}{Mentored a Computer Engineering undergraduate who was helping with software engineering of my soft robot model.}{}
		
	\cvline{Fall 2015}{Mentored a Computer Engineering Masters student who was taking an independent research credit with Nick Gans.}{}
	\fi
			
	\section{Awards and honors}
	\cvlistitem{\textbf{PTDF Overseas Scholarship Award [Nigeria]} \qquad \quad $\sim$1.7\% acceptance, \hspace{0.9cm} 2011 - 2012.}
	%\cvitem{}{ \pounds 25,500 for one year}			
	\cvlistitem{\textbf{Ericsson Graduate Fellowships} \hspace{6.5cm} 2015 - Present.}			
	%\cvitem{}{}		
	\cvlistitem{\textbf{Jonsson Scholarship} \hspace{8.8cm} 2014 - 2015}	
	%\cvitem{}{}		
	%	\cvlistitem{\textbf{Achievement Awardee, University of Florida} \qquad \qquad \emph{\{\textbf{Offered: \$4,500}\}} \qquad  \qquad Fall 2014}	
	%	\cvitem{}{ %\footnotesize Partial tuition waiver for up to three semesters to the Mechanical and Aerospace Engineering Department's Graduate Program based on academic record of achievement in undergraduate degree. \emph{\{\textbf{Offered: \$4,500}\}}.
	%		}		
	\cvlistitem{\textbf{Federal Government (of Nigeria) Scholarship}, \hspace{1.0cm}  $\sim$3.6\%  acceptance,\hspace{1.5cm}	2002.}
	%\cvitem{}{}	 % \emph{\textbf{N50,000 per annum}}.	
	\cvlistitem{\textbf{Ondo State (Nigeria) Scholarship}, \hspace{2.7cm} $\sim$10\% acceptance, \hspace{2.1cm} 2004. %\newline \emph{\textbf{N25,000}} per annum.
	}
		
	\section{Computing}
	\cvitem{\textcolor{light-blue}{High-level}}{\textbf{C++, Python, MATLAB, Lua, Torch} and \textbf{LabVIEW}. See my github profiles (\href{https://github.com/lakehanne}{\textcolor{light-blue}{github.com/lakehanne}} \& \href{https://github.com/service-lab}{\textcolor{light-blue}{github.com/service-lab}}) for details.} 
	%\cvitem{\textcolor{light-blue}{Linux}}{Linux distros: OpenSuse, Ubuntu and other debian distros.}
			
	\cvitem{\textcolor{light-blue}{ROS}}{ ROS Distros: ROS Hydro, Indigo and Jade.
	 \newline
	ROS Protocols: Xacro, URDF and RViZ.}
		
	\cvitem{\textcolor{light-blue}{Web}}{\textcolor{light-blue}{Jekyll}, \textcolor{light-blue}{Hyde}, \textcolor{light-blue}{Markdown} and \textcolor{light-blue}{HTML}.}
	
	\iffalse
	\cvitem{\textcolor{light-blue}{SciPy}}{ SciPy tools: \textcolor{light-blue}{matplotlib}, \textcolor{light-blue}{numpy}, \textcolor{light-blue}{scikit learn} and the \textcolor{light-blue}{pandas} library.}
	
	\cvitem{\textcolor{light-blue}{Machine Learning}}{Sci-kit learn, pybrain, torch, and lua libraries.}
	\fi
	\section{Selected service and leadership}
	\cventry{2016--Present}{Member}{IEEE Boston}{Greater Boston Area and New England, USA}{}{}
		
	\cventry{2015 -- 2016}{Science instructor}{IEEE Dallas Shoulder of Giants Workshops}{Dallas, TX}{}{Regular participant at IEEE Dallas Young Professionals community outreaches}
	
	\cventry{Summer 2015}{Summer Science Program}{University of Texas at Dallas}{Richardson, TX}{}{Trained high-school kids in basic robots control and programming with the Berkeley Snap! kit and arduino.}
	
	\cventry{2011 - 2013}{Team Lead}{Engineers Without Borders, University of Sheffield Chapter}{Sheffield, England}{}{Co-designed the ‘Sustrans trailer’, and helped in the modeling of system components and calculation of optimal parameters used to maximize power output from the Haley farm electric generator.}
	
	\cventry{Fall 2012}{Workshop participant}{ILA Berlin Airshow}{Berlin, Germany}{}{Selected by Cassidian (an EADS company) for the \emph{Aerospace Systems Engineering} workshop based on a competitive admission process.}
	
	\cventry{Summer 2012}{Workshop participant}{Farnborough International Airshow}{NE Hampshire, England}{}{Selected by Airbus (an EADS company) among participants at the \emph{UAV and Fighter Aircraft} workshop based on a competitive admission process.}
	
	\section{Other interests and activities}
	
	\cvline{}{Most-viewed writer in Control Engineering, \textbf{\textit{Quora}}
	\newline
	\textsf{-- Oct/Nov. 2015; March 2016 - Present}}{}
	
	\renewcommand{\listitemsymbol}{-}
	\clearpage
	%-----       letter       ---------------------------------------------------------
	% recipient data
%	\recipient{Company Recruitment team}{Company's name\\Street address\\Zip Code City}
%	\date{Date}
%	\opening{Dear Sir or Madam,}
%	\closing{Yours faithfully,}
%	\enclosure{enclosures}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%	\makelettertitle
%	\makeletterclosing

\end{document}
