%% start of file `template_en.tex'.
%% Copyright 2006-1008 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\PassOptionsToPackage{pdfpagelabels=false}{hyperref} 
\documentclass[10pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[blue, modroman]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

	
\usepackage[sc]{mathpazo}
\linespread{1.05}
\usepackage[T1]{fontenc}
%\usepackage[dvipsnames]{xcolor}

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using
%\usepackage{hyperref}
% adjust the page margins
\usepackage[scale=0.8]{geometry}
%\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

\setlength{\topmargin}{-0.7in}
\usepackage{calc}
\setlength{\textheight}{\textheight+0.5in}
\usepackage{layout}
%\usepackage{hyperref}
\usepackage{color}
%\hypersetup{linkbordercolor = green}
%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Olalekan}
\familyname{Ogunmolu}
\definecolor{light-blue}{rgb}{0.30,0.35,1}
\title{Control Systems | Robotics | Machine Learning \newline
\textbf{\textcolor{light-blue}{\footnotesize 
Rerum Cognoscere Causas: To know the causes of things.} }}                               % optional, remove/comment the line if not wanted
\address{ATC 1.801, ATEC Bldg}{UT Dallas, Richardson, TX 75080}         % optional, remove/comment the line if not wanted; the "country" arguments can be omitted or provided empty 
%\fax{fax number}                             % optional, remove/comment the line if not wanted
\email{patlekano@gmail.com}  
%\mobile{omitted intentionally}                             % optional, remove/comment the line if not wanted
%\homepage{http://lakehanne.github.io}                         % optional, remove/comment the line if not wanted
%\extrainfo{\footnotesize http://ecs.utdallas.edu/$\sim$olalekan.ogunmolu/} 
\extrainfo{\footnotesize http://ecs.utdallas.edu/ $\sim$ opo140030}                 % optional, remove/comment the line if not wanted
%\photo[64pt][0.4pt]{EverPat}                       % optional, uncomment the line if wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Rerum Cognoscere Causas: To know the causes of things.}                                  % optional, remove/comment the line if not wanted
%

	
	
\begin{document}
	\long\def\/*#1*/{}								% Define block comment
%\vspace{-2ex}
	%-----       resume       ---------------------------------------------------------
	\makecvtitle
	\section{Research Thrusts}
	\cvitem{}{Data-Driven Control. Robotic visual perception. Machine Learning. Hardware integration.}
	
	\section{Education}
	\cventry{2014--Present}{PhD in Electrical Engineering }{University of Texas at Dallas}{Richardson}{United States}
	{Advisor: Nick Gans. Design and prototype of a medical soft robot for automated patient positioning during cancer radiotherapy. {}   } % arguments 3 to 6 can be left empty
	
	\cventry{2011--2012}{Master of Science in Engineering in Control Systems}{The University of Sheffield}{Sheffield}{United Kingdom}{Advisor: Tony J. Dodd. Thesis: ``\href{http://lakehanne.github.io/downloads/MS_Thesis.pdf}{\textcolor{blue}{Autonomous Navigation of a Rotorcraft Unmanned Aerial Vehicle using Machine Vision}}.'' | Committee Members: Drs. George Panoutsos and Robin Pursehouse. | Dissertation reviewed by Prof. Mahdi Mahfouf.}
	
	\cventry{2000--2005}{Bachelor Of Science in Physics \& Electronics}{Adekunle Ajasin University}{Akungba}{Nigeria}{\href{http://lakehanne.github.io/downloads/BS_Thesis.pdf}{\textcolor{blue}{Senior thesis}} advised by Ademola Amusa (\emph{MS, Columbia University, PhD UIUC}).| Dissertation Grade: 85\% $\equiv$ A+ | Graduated Magna Cum Laude.}

	\section{Publications}
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/ACC2016/ACC2016.pdf}{\textcolor{blue}{Nonlinear Systems Identification Using Deep Dynamic Neural Networks}}. To appear in: \emph{American Control Conference (ACC)}, Seattle, WA. May 2017.}{}
		
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2016/CASE2016.pdf}{\textcolor{blue}{Vision-based control of a soft-robot for Maskless Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Fort-Worth, Texas, August 2016. %\newline
	 DOI: 10.1109/CoASE.2016.7743378}{}
		
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Xuejun Gu, Steve Jiang, and Nick Gans. \href{http://ecs.utdallas.edu/~opo140030/media/Papers/CASE2015/CASE2015.pdf}{\textcolor{blue}{A Real-Time Soft-Robotic Patient Positioning System for Maskless Head-and-Neck Cancer Radiotherapy}}. \emph{IEEE Conference on Automation Science and Engineering (CASE)}, Gothenburg, Sweden, August 2015. DOI: 10.1109/CoASE.2015.7294318}{}
	
	\cvitem{}{\textbf{Olalekan Ogunmolu}, Nick Gans, Steve Jiang, Xuejun Gu. \href{http://www.aapm.org/meetings/2015AM/PRAbs.asp?mid=99&aid=29621}{\textcolor{blue}{An Image-Guided Soft Robotic Patient Positioning System for Maskless Head-And-Neck Cancer Radiotherapy: A Proof-of-Concept Study}}. \emph{American Association of Physicists in Medicine (AAPM)} Annual Meeting, July 2015.}{}
	
	\cvitem{}{\textbf{Olalekan Ogunmolu}, %\href{http://lakehanne.github.io/downloads/MS_Thesis.pdf}
	{\textcolor{black}{Autonomous Navigation of a Rotor-craft unmanned aerial vehicle using machine vision.}} . \newline {MS Thesis, August. 2011. Advisor: Tony J. Dodd, University of Sheffield, England.}}{}
		
	\cvitem{}{\textbf{Olalekan Ogunmolu}, \href{http://lakehanne.github.io/downloads/BS_Thesis.pdf}{\textcolor{blue}{Single Fractional Parentage Coefficients in the sd-Shell Nuclei}} . \newline {BS Thesis, Nov. 2004. \hspace{0.5em} Advisor: Ademola Amusa, Adekunle Ajasin University, Nigeria.}}{}

	
	\section{Invited Talks}
	\cvitem{UTSW}{Soft-Robotic Adaptive Neuro-Controllers for Head and Neck Positioning in Cancer Radiotherapy,  \emph{Physics Research Seminar Series, UT Southwestern Medical Center} Dallas, TX, USA. January 2017.}
		
	\cvitem{IEEE}{Towards automated accurate patient positioning in maskless cancer radiotherapy. \emph{IEEE Computational Intelligence Society,} UT Arlington, TX, USA. December 2015.}
	
	\section{Experience}
	\subsection{Research}
	\cventry{Summer 2016}{\textbf{Hardware Integration Intern,  Amazon Robotics, North Reading} }{}{MA}{
	\newline
	$\bullet$ Wrote and deployed the SLAM algorithm for the Zeus mobile robot project.
	\newline
	$\bullet$ Integrated Amazon Echo's \textsf{Alexa} on the Hermes robot (this mapped and roamed the Amazon Robotics (AR) building, taking orders from employees while navigating the AR offices).
	\newline 
	$\bullet$ Designed and integrated the software architecture for a web-based \textsf{ client and server} system for the Hermes mobile robot project that allowed remote real-time \textsf{node.js-based} command of the Hermes robot
	}{}
			
	\cventry{Spring '16 \newline \footnotesize}{\textbf{Hardware Integration Intern, Advanced Robotics Lab, Amazon Robotics LLC}}{North Reading, MA}{}{	\/* \footnotesize A wholly owned Amazon.com Subsidiary.*/}{
	$\bullet$ Wrote the ROS codebase for GYGES Stations line scanners. % used in robots' pick and place tasks. 	
	\newline $\bullet$ Wrote test cases, and defined test procedures for 2D and 3D sensors required on the new stow and sort robot development stations at Amazon Fulfillment Centers.	
	\newline
	$\bullet$ Contributed wikis  to the kiva Systems confluence webpage and a model predictive controller "HowTO" to the kiva Systems knowledge base.	
	\newline
	$\bullet$ Modeled and designed 3-D sensor plates test material in hand sketches and SolidWorks
			%·      Analyze components and systems using standard tools including SolidWorks Simulation (FEA) as well as hand calculations
%	\textbf{Job Description:}   Work as part of an interdisciplinary team to design and analyze mechanisms, modules or systems
%	·      Model and detail solutions in hand sketches and SolidWorks
		%·      Analyze components and systems using standard tools including SolidWorks Simulation (FEA) as well as hand calculations
%		·      Design and code firmware architecture for prototype development
%		·      Define requirements for, specify and find components for prototype parts
%		·      Lead design reviews
%		·      Build models and prototypes
%		·      Conduct testing
%		·      Support staff writing specifications and plans.
		}{}
		
		
			
		\cventry{Fall '14 - Spring '15}{\textbf{Research Assistant, Sensing, Robotics, Vision, Control, and Estimation (SeRViCE) Lab}}{University of Texas at Dallas}{}{}{
	%	\newline
		$\bullet$ Evaluation and determination of overall system requirements for proof-of-concept design of soft-robot system to be used in \textbf{intensity modulated radiotherapy (IMRT)}
		\newline
		$\bullet$ Procurement and integration of mechanical hardware, vision components and software design for controlling patient head motion during IMRT simulation.}
		
		%\newline
		%$\bullet$ Implemented a classical control algorithm that mobilized patient head and neck 1-DOF motion during IMRT up to 5mm accuracy}
		
		%\cventry{Summer - Fall '15}{\textbf{Research Assistant, Sensing, Robotics, Vision, Control, and Estimation (SeRViCE) Lab}}{University of Texas at Dallas}{}{}{
	%	\newline 
	%	$\bullet$ Achieved a sub-millimeter accuracy using multisensor kalman fusion in head motion tracking; optimized and parallelized algorithm in CUDA to speed up real-time head motion detection rates
		%\newline
		%$\bullet$ Implemented an LQG controller in LabVIEW based on the kalman filter estimate and achieved $\pm$1.5mm accuracy at head and neck 1-DOF motion control in clinical radiotherapy
		%\newline
		%$\bullet$ (Fall 2015)Developed ROS codebase for head motion sensing using the Vicon motion capture system}
		%\fi
			
		\subsection{Teaching}
		\cventry{Fall '14 - '16}{Teaching Assistant, \textbf{Introduction to Robotics}}{University of Texas at Dallas}{}{}{Guided students during laboratories in programming the Robai Cyton 300R2 Robot and graded homeworks.}
					
		\cventry{Spring '15}{\textbf{Teaching Assistant, Linear Systems (M.S. Class)}}{University of Texas at Dallas}{}{}{Responsible for helping Masters students with linear control theory applications; graded homeworks and midterms.}
			
		\cventry{Spring '14}{\textbf{Instructor, Analysis and Design of Digital Systems}}{Adekunle Ajasin University}
		{}{}{Developed course modules, sole instructor for sophomore students, graded homeworks, designed and graded exams.}			
		
		\cventry{Summer '14}{\textbf{Instructor, Digital Logic Design}}{Adekunle Ajasin University}{}{}{Co-developed course modules, joint-instructor for junior students, graded homeworks, designed and graded exams.}
				
		\cventry{Summer '14}{\textbf{Instructor, Introduction to Assembly Language}}{Adekunle Ajasin University}{}{}{Developed course modules, sole instructor for sophomore students, graded homeworks, designed and graded exams.}
		
		\subsection{Miscellaneous}
	%	\cventry{2007--2008}{Banking Assistant}{First Bank of Nigeria Plc}{Lagos}{}{Provided IT infrastructure support for Broad Street branch (Lagos); resolved customer queries; managed key branch accounts.}
		
		\cventry{2005--2007}{System Engineer}{DMT Technologies Limited}{KD}{Nigeria}{Managed E-1 Links for Mobile TelCo Customers; Installed RF communication stations, Deployed and configured networking devices.}
	
		\cventry{2009--2011}{\textbf{Warehouse Manager, Apapa Plant}}{Coca-Cola Hellenic Bottling Company Plc}{Lagos}{}{Managed the basic and depot warehouses which accounted for 30\% of company's storage depots for finished goods and raw materials. Designed protocols and procedures that reduced logistics costs by 10\% company-wide.}
		
		\section{Mentoring}
		\subsection{Research mentoring}
		\cvline{Fall 2016}{Alex Tomkovich: Computer Engineering Junior.}{}
		
		\cvline{Fall 2015}{Ajith Venkateswaran: Computer Engineering Masters student. Currently at Samsung Research, America.}{}
				
		\cvline{Spring 2015}{Grant Carr: Computer Engineering Junior.}{}	
		
		\section{Languages}
		\cvitemwithcomment{English}{Can read, write and speak fluently.}{Lived in Nigeria, United Kingdom and United States.}
		
		\cvitemwithcomment{Yoruba}{Proficient}{Native Nigerian Language. Spoken at home.}

	\section{Awards and honors}	
	%\iffalse
	\cvlistitem{\textbf{Invited Member, Golden Key International Honour Society} \hspace{5.5em} October 2016}			
	\cvitem{}{\footnotesize Ranked among the top 15\% of students at the University of Texas at Dallas. %\emph{\textbf{\$3,000 per annum}}.
			}
	%\fi
	\cvlistitem{\textbf{IEEE RAS Travel Award} \hspace{7.5cm} August 2016}			
	\cvitem{}{\footnotesize IEEE Robotics and Automation Society student travel award to CASE-ISAM 2016. %\emph{\textbf{\$3,000 per annum}}.
		}
			
	\cvlistitem{\textbf{Ericsson Graduate Fellowship} \hspace{6.5cm} 2015 - 2016.}			\cvitem{}{\footnotesize Merit-based graduate fellowship for full-time graduate students in electrical engineering with a proven track record of academic excellence as evidenced by research, GPA and courses completed. %\emph{\textbf{\$3,000 per annum}}.
		}
		
	\cvlistitem{\textbf{Jonsson Scholarship} \hspace{8.8cm} 2014 - 2015}	
	\cvitem{}{\footnotesize Competitive, merit-based scholarships awarded to new graduate students with proven published research, excellent GPA and GRE scores.}
		
	\cvlistitem{\textbf{Achievement Award, University of Florida, } %\emph{\{\textbf{Offered: \$4,500}\}} 
	   \textit{(Declined)} \qquad \qquad \qquad \qquad \qquad \quad Fall 2014 \newline
	   Mech \& Aerospace Engineering Dept.}	
		
	\cvlistitem{\textbf{PTDF Overseas Scholarship Award [Nigeria]} \qquad \quad $\sim$1.7\% acceptance, \hspace{0.9cm} 2011 - 2012.}
	\cvitem{}{\footnotesize Competitive, merit-based scholarships awarded to best 5 students from each state in the country. Second ranked awardee from my state in nation-wide tests. \emph{\textbf{\pounds25,500+ for one year}.}}

	%	\cvitem{}{ %\footnotesize Partial tuition waiver for up to three semesters to the Mechanical and Aerospace Engineering Department's Graduate Program based on academic record of achievement in undergraduate degree. \emph{\{\textbf{Offered: \$4,500}\}}.
	%		}
		
	\cvlistitem{\textbf{Federal Government (of Nigeria) Scholarship}, \hspace{1.0cm}  $\sim$3.6\%  acceptance,\hspace{1.5cm}	2002.}
	\cvitem{}{\footnotesize Competitive, merit-based scholarships awarded to best Nigerian students based on performance in questions relating to science and engineering. \emph{\textbf{N50,000 per annum}}.}
		
	\cvlistitem{\textbf{Ondo State (Nigeria) Scholarship}, \hspace{2.4cm} $\sim$10\% acceptance, \hspace{2.4cm} 2004.}
	\cvitem{}{Merit-based scholarship for Ondo state students with excellent academic achievement and honors grade. \emph{\textbf{N25,000}} per annum.} 
		
	\section{Computing}
	\cvitem{\textcolor{light-blue}{Programming}}{ C++, Torch/Lua, MATLAB/LabVIEW, Python -- in that order. \newline
	\textbf{\textendash \, C++: } \textsf{the point cloud, opencv, boost, eigen libraries; c++11/14 standards}.
	\newline
	\textbf{\, \textendash \, Torch 7:} \textsf{\textcolor{light-blue}{cutorch}, \textcolor{light-blue}{cudnn}, \textcolor{light-blue}{cunn}, the \textcolor{light-blue}{display, rnn and conv-net} libraries}
	\newline 
	\textbf{\, \textendash \, MATLAB}, \textbf{LabVIEW}: \textsf{system identification, control, signal processing, fpga, robotics modules/toolkits}
	\newline
	\textbf{\, \textendash \,Python:} \textsf{Familiar with sciPy tools including: \textcolor{light-blue}{matplotlib}, \textcolor{light-blue}{numpy}, \textcolor{light-blue}{scikit learn}}.} 

	\cvitem{\textcolor{light-blue}{*Nix OSes}}{Ubuntu, Debian. Familiar with openSUSE.}
			
	\cvitem{\textcolor{light-blue}{ROS}}{
	ROS Hydro/Indigo/Jade/Kinetic for vision, estimation, function approximation, and control tasks.
    \textbf{Visualization and Robot Protocol Tools: }\textsf{\textcolor{light-blue}{Xacro, URDF, and RViZ.}}}
		
	\cvitem{\textcolor{light-blue}{\small Web}}{\textcolor{light-blue}{\small HTML}, \textcolor{light-blue}{\small Markdown, socket.io, node.js, express.js, } \textcolor{light-blue}{\small Jekyll/Ruby/Hyde}.}
	\cvitem{\textcolor{light-blue}{\small Github} }{ \href{https://github.com/lakehanne}{\textcolor{light-blue}{https://github.com/lakehanne}} | \href{https://github.com/service-lab}{\textcolor{light-blue}{https://github.com/service-lab}}
		}
	\cvitem{\textcolor{light-blue}{\small Gitlab} }{ \href{https://gitlab.kitware.com/lakehanne}{\textcolor{light-blue}{https://gitlab.kitware.com/lakehanne}} 
			}
	\cvitem{\textcolor{light-blue}{\small Windows}}{\small MS DOS, Win XP, 7, 8, \& 10.}
%\iffalse	
	\section{Select OpenSource Projects}	 
	 \cvitem{\href{https://github.com/element-research/rnn}{\textcolor{light-blue}{RBN}}}{Recurrent Batch Normalization of Neural Networks in Torch7. (Available at \href{https://github.com/element-research/rnn}{\textcolor{light-blue}{https://github.com/element-research/rnn}})
	 	}
	 	
 	 \cvitem{\href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{GPS}}}{Catkinized version of Levine et. al's guided policy search algorithm in ROS Indigo (Available at \href{https://github.com/lakehanne/gps}{\textcolor{light-blue}{https://github.com/lakehanne/gps}}).
 	 }
 	 
 	 \cvitem{\href{https://github.com/lakehanne/nn/blob/master/DICECriterion.lua}{\textcolor{light-blue}{DICE}}}{S\o{}rensen-Dice coefficients in Torch7. (Available at  \href{https://github.com/lakehanne/nn}{\textcolor{light-blue}{https://github.com/lakehanne/nn}). 
 	  	 	}}	
 	  	 
  	\cvitem{\href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{Savgol}}}{C++ Implementation of Savitzky-Golay Differentiation Coefficients and Filters. (Available at \href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{https://github.com/lakehanne/savitzky-golay}})%(Available on \href{https://github.com/lakehanne/savitzky-golay}{\textcolor{light-blue}{https://github.com/lakehanne/savitzky-golay}})
  	}
   
 	\cvitem{\href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{FARNNs}}}{Training of multilayer networks, simple recurrent neural networks, long short-term memory cells (with peep-hole connections), fast LSTMS, %(which are LSTMs with gates computed in one fell-swoop
 	and recurrent batch normalized FastLSTMs to model the relationship between Borel measurable sets. (Available at  \href{https://github.com/lakehanne/FARNN}{\textcolor{light-blue}{https://github.com/lakehanne/FARNN})
 	}} 	
 
 	\cvitem{\href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{Keyence}}}{Minimal source code for retrieving profile map from the keyence LJV-7000 series line scanners. (Available at  \href{https://github.com/lakehanne/keyence}{\textcolor{light-blue}{https://github.com/lakehanne/keyence}) 
 	}}
 	
 	\cvitem{An all-convolutional network}{Source codes for my entry in the Kaggle 2016 data science competition in identifying and segmenting ultrasound images of the human neck. Codes available upon request.}
 	
	\section{Selected service and leadership}
	\cventry{2016--present}{Member}{IEEE Boston}{Greater Boston, USA}{}{}
	
	\cventry{2015 -- 2016}{Science instructor}{IEEE Dallas Shoulder of Giants Workshops}{Dallas, TX}{}{Participant at IEEE Dallas Young Professionals community outreaches in promoting STEM education and awareness in the Dallas/Fort-Worth Metroplex.}
	
	\cventry{Summer 2015}{Summer Science Program}{University of Texas at Dallas}{Richardson, TX}{}{Trained high-school kids in basic robots control and programming with the Berkeley Snap! kit and arduino.}
	%\iffalse
	%\cventry{2011 - 2013}{Team Lead}{Engineers Without Borders, University of Sheffield Chapter}{Sheffield, England}{}{Co-designed the ‘Sustrans trailer’, and helped in the modeling of system components and calculation of optimal parameters used to maximize power output from the Haley farm electric generator.}
%	\fi
	\cventry{Fall 2012}{Workshop participant}{ILA Berlin Airshow}{Berlin, Germany}{}{Selected by Cassidian (an EADS company) for the \emph{Aerospace Systems Engineering} workshop. % based on a competitive admission process.
	}
	
	\cventry{Summer 2012}{Workshop participant}{Farnborough International Airshow}{NE Hampshire, England}{}{Selected by Airbus (an EADS company) among participants at the \emph{UAV and Fighter Aircraft} workshop. % based on a competitive admission process.
	}
	
	\section{Other interests and activities}
	\cvline{}{Most-viewed writer in ROS, \textbf{\textit{Quora}} \hspace{12.5em}
	%\newline 
	\textsf{ June - August 2016}}{}
	
	\cvline{}{Most-viewed writer in Control Engineering, \textbf{\textit{Quora}}
%	\newline
	\textsf{ Oct/Nov. 2015; March - April 2016}}{}
	

	\cvline{}{Teacher Badge \hspace{8.0em}\textbf{\textit{Stackoverflow.com}}
	%	\newline
	\hspace{8.0em}\textsf{2015 -- Present}}{}
	
	\cvline{}{Scholar Badge \hspace{8.0em}\textbf{\textit{Stackexchange.com}}
		%	\newline
	\hspace{8.0em}\textsf{2015 -- Present}}{}
	\renewcommand{\listitemsymbol}{-}
	\clearpage
	%-----       letter       ---------------------------------------------------------
	% recipient data
%	\recipient{Company Recruitment team}{Company's name\\Street address\\Zip Code City}
%	\date{Date}
%	\opening{Dear Sir or Madam,}
%	\closing{Yours faithfully,}
%	\enclosure{enclosures}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%	\makelettertitle
%	\makeletterclosing

\end{document}
